---
title: "NASA Dataset Final Project"
author: "David Han"
date: "6/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, eval = TRUE,
  out.width = "100%", dpi = 120,
  fig.align = "center", cache = FALSE
)
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(highcharter))
suppressPackageStartupMessages(library(leaflet))
suppressPackageStartupMessages(library(corrplot))
suppressPackageStartupMessages(library(modelr))
suppressPackageStartupMessages(library(broom))
suppressPackageStartupMessages(library("ggpubr"))
library(plotly)
dfnasa <- as.data.frame(nasa)
year1 = slice(dfnasa,1,577,1153,1729,2305,2881,3457,4033,4609,5185,5761,6337)
year2 = slice(dfnasa,6913,7489,8065,8641,9217,9793,10369,10945,11521,12097,12673,13249)
year3 = slice(dfnasa,13825,14401,14977,15553,16129,16705,17281,17857,18433,19009,19585,20161)
year4 = slice(dfnasa,20737,21313,21889,22465,23041,23617,24193,24769,25345,25921,26497,27073)
year5 = slice(dfnasa,27649,28225,28801,29377,29953,30529,31105,31681,32257,32833,33409,33985)
year6 = slice(dfnasa,34561,35137,35713,36289,36865,37441,38017,38593,39169,39745,40321,40897)
combine = rbind(year1,year2,year3,year4,year5,year6)
combine <- as.data.frame(combine)
```

##Linear Regressions
I created several linear regression models using temperature as the dependent variable. 

####Temperature vs. Low Cloud Coverage
```{r}
temp_lowc <- lm(temperature ~ cloudlow,data = combine)
temp_lowc %>% tidy() %>% as.data.frame()
lowcg <- ggplot(combine,aes(x=cloudlow,y=temperature))+geom_point()+
  xlab("Low Cloud Coverage")+ylab("Temperature")+
  geom_abline(intercept=277.7133,slope=0.6569,col="red")
lowcg
```

####Temperature vs. Middle Cloud Coverage
```{r}
temp_midc <- lm(temperature ~ cloudmid,data = combine)
temp_midc %>% tidy() %>% as.data.frame()
midcg <- ggplot(combine,aes(x=cloudmid,y=temperature))+geom_point()+
  xlab("Middle Cloud Coverage")+ylab("Temperature")+
  geom_abline(intercept=313.376,slope=-1.168,col="red")
midcg
```

####Temperature vs. High Cloud Coverage
```{r}
temp_highc <- lm(temperature ~ cloudhigh,data = combine)
temp_highc %>% tidy() %>% as.data.frame()
highcg <- ggplot(combine,aes(x=cloudhigh,y=temperature))+geom_point()+
  xlab("High Cloud Coverage")+ylab("Temperature")+
  geom_abline(intercept=298.8933,slope=-0.8519,col="red")
highcg
```

####Temperature vs. Ozone
```{r}
temp_ozone <- lm(temperature ~ ozone,data = combine)
temp_ozone %>% tidy() %>% as.data.frame()
ozoneg <- ggplot(combine,aes(x=ozone,y=temperature))+geom_point()+
  xlab("Ozone Level")+ylab("Temperature")+
  geom_abline(intercept=337.8292,slope=-0.1526,col="red")
ozoneg
```

####Temperature vs. Surface Temperature
```{r}
temp_surftemp <- lm(temperature ~ surftemp,data = combine)
temp_surftemp %>% tidy() %>% as.data.frame()
surfg <- ggplot(combine,aes(x=surftemp,y=temperature))+geom_point()+
  xlab("Surface Temperature")+ylab("Temperature")+
  geom_abline(intercept=86.0301,slope=0.7002,col="red")
surfg
```

####Temperature vs. Pressure
```{r}
temp_pres <- lm(temperature ~ pressure,data = combine)
temp_pres %>% tidy() %>% as.data.frame()
presg <- ggplot(combine,aes(x=pressure,y=temperature))+geom_point()+
  xlab("Atmospheric Pressure")+ylab("Temperature")+
  geom_abline(intercept=259.84484,slope=0.03408,col="red")
presg
```

<br><br>

Used to combine all graphs into one figure.
```{r}
figure <- ggarrange(lowcg,midcg,highcg,ozoneg,surfg,presg ,ncol = 3,nrow=2)
figure
```


##Regression with Multiple Variables

From the linear regressions, pressure was the only variable that did not correlate with temperature. Therefore, the multiple linear regression model will not use that variable for predictions.

```{r}
model <- lm(temperature ~ cloudlow+cloudmid+cloudhigh+ozone+surftemp,data=combine)
summary(model)
```

##Predictions

Chose 50 random data points from the NASA data set (some listed below):

```{r}
temp_pred <- sample_n(dfnasa,50) 
head(temp_pred)
```
Data frame of 50 random rows from the NASA data set.
<br>
```{r}
model_usage <- temp_pred %>% select(cloudhigh,cloudlow,cloudmid,ozone,surftemp)
real_temp <- temp_pred %>% select(temperature)

head(model_usage)
```
The model_usage variable was used to find the prediction while storing the actual temperature in real_temp.
<br>
```{r}
model_predictions <- model_usage %>% add_predictions(model)

head(model_predictions)
```

####Graph of Predictions

```{r}
actual_preddf <- data.frame(cbind(real_temp, model_predictions$pred))
colnames(actual_preddf) = c("real","prediction")

ggplotly(ggplot(actual_preddf)+geom_point(aes(x=real,y=prediction))+
  geom_abline(intercept=0,slope=1,col="darkturquoise",size=1)+
  xlab("Real Temperature")+ylab("Predicted Temperature"))
```
<br>


