---
title: "NASA Dataset Final Project"
author: "David Han"
date: "6/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(highcharter))
suppressPackageStartupMessages(library(leaflet))
dfnasa <- as.data.frame(nasa)
year1 = slice(dfnasa,1,577,1153,1729,2305,2881,3457,4033,4609,5185,5761,6337)
```
##NASA Spatio-temporal Data

The data are geographic and atospheric measures on a very coarse 24 by 24 grid covering Central America. The data was obtained from the NASA Langley Research Center - Atmospheric Science Data Center.

##Storage

The data was stored in a data cube tbl from the dplyr package (tbl_cube). This type of data storage uses two arguments: dimensions and measures. The dimensions is a named list of vectors while measures is a named list of arrays.

Dimensions - latitude, longitude, month, and year.

Measures - Cloud coverage, ozone, surface temperature, temperature, and pressure.

```{r}
summary(nasa)
```

## Variables


####Latitude/Longitude

####Month/Year

####Cloud Coverage

####Ozone

####Pressure

####Temperature

####Surface Temperature


